Fast Sorting on Modern Computers

### 2005-07-12 docs/tech_report/result_list.tex
removed word gonnet from document
managed to compile the docs, without the 16 byte cache line
updated gnuplot scripts, added scripts for newer sorts updated docs to inculde new sorts in the result list fixed bw

\label{result_list}
\afterpage{
\smallplot{on2_insertsort}{insertion sort}{}{}{}{}{}
\smallplot{on2_selectsort}{selection sort}{}{}{}{}{}
\smallplot{on2_bubblesort}{bubblesort}{}{}{}{}{}
\smallplot{on2_bubblesort2}{bubblesort2}{}{}{}{}{}
\smallplot{on2_shakersort}{shakersort}{}{}{}{}{}
\smallplot{on2_shakersort2}{shakersort2}{}{}{}{}{}
%
\smallplot{base_heapsort}{base heapsort}{}{}{}{}{}
\smallplot{cache4_heapsort}{cache heapsort (4-heap)}{}{}{}{}{}
\smallplot{cache4_heapsort_small_cache_line}{cache heapsort (4-heap) (with 16-byte cache line)}{}{}{}{}{}
\smallplot{cache_heapsort}{cache heapsort (8-heap)}{}{}{}{}{}
%
\smallplot{algorithm_n}{algorithm N}{}{}{}{}{}
\smallplot{algorithm_s}{algorithm S}{}{}{}{}{}
\smallplot{base_mergesort}{base mergesort}{}{}{}{}{}
\smallplot{double_tiled_mergesort}{double tiled mergesort}{}{}{}{}{}
\smallplot{double_multi_mergesort}{double multi-mergesort}{}{}{}{}{}
%
\smallplot{base_quicksort}{base quicksort}{}{}{}{}{}
\smallplot{cache_quicksort}{memory-tuned quicksort}{}{}{}{}{}
\smallplot{multi_quicksort}{multi-quicksort (binary search)}{}{}{}{}{}
\smallplot{multi_quicksort_seq}{multi-quicksort (sequential search)}{}{}{}{}{}
%
\smallplot{base_radixsort}{base radixsort}{}{}{}{}{}
\smallplot{cache_radixsort}{cache radixsort}{}{}{}{}{}
%
\smallplot{gonnet_shellsort}{gonnet shellsort}{}{}{}{}{}
\smallplot{improved_gonnet_shellsort}{improved gonnet shellsort}{}{}{}{}{}
}

>>>>

\label{result_list}
\afterpage{
\smallplot{on2_insertsort}{insertion sort}{}{}{}{}{}
\smallplot{on2_selectsort}{selection sort}{}{}{}{}{}
\smallplot{on2_bubblesort}{bubblesort}{}{}{}{}{}
\smallplot{on2_bubblesort2}{improved bubblesort}{}{}{}{}{}
\smallplot{on2_shakersort}{shakersort}{}{}{}{}{}
\smallplot{on2_shakersort2}{improved shakersort}{}{}{}{}{}
%
\smallplot{base_heapsort}{base heapsort}{}{}{}{}{}
\smallplot{cache4_heapsort}{cache heapsort (4-heap)}{}{}{}{}{}
\smallplot{cache_heapsort}{cache heapsort (8-heap)}{}{}{}{}{}
%
\smallplot{algorithm_n}{algorithm N}{}{}{}{}{}
\smallplot{algorithm_s}{algorithm S}{}{}{}{}{}
\smallplot{base_mergesort}{base mergesort}{}{}{}{}{}
\smallplot{tiled_mergesort}{tiled mergesort}{}{}{}{}{}
\smallplot{multi_mergesort}{multi-mergesort}{}{}{}{}{}
\smallplot{double_tiled_mergesort}{double tiled mergesort}{}{}{}{}{}
\smallplot{double_multi_mergesort}{double multi-mergesort}{}{}{}{}{}
%
\smallplot{base_quicksort1}{base quicksort (no median)}{}{}{}{}{}
\smallplot{base_quicksort}{base quicksort (median-of-3)}{}{}{}{}{}
\smallplot{base_quicksort5}{base quicksort (pseudo-median-of-5)}{}{}{}{}{}
\smallplot{base_quicksort7}{base quicksort (pseudo-median-of-7)}{}{}{}{}{}
\smallplot{base_quicksort9}{base quicksort (pseudo-median-of-9)}{}{}{}{}{}
\smallplot{cache_quicksort}{memory-tuned quicksort}{}{}{}{}{}
\smallplot{multi_quicksort}{multi-quicksort (binary search)}{}{}{}{}{}
\smallplot{multi_quicksort_seq}{multi-quicksort (sequential search)}{}{}{}{}{}
%
\smallplot{base_radixsort}{base radixsort}{}{}{}{}{}
\smallplot{cache_radixsort}{cache radixsort}{}{}{}{}{}
\smallplot{aligned_cache_radixsort}{aligned cache radixsort}{}{}{}{}{}
%
\smallplot{shellsort}{shellsort}{}{}{}{}{}
\smallplot{improved_shellsort}{improved shellsort}{}{}{}{}{}
}
